\documentclass{article}
\usepackage{geometry}
\usepackage{lipsum}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[english]{babel}
\usepackage{microtype}
\usepackage{textcomp}
\usepackage{newtxtext}
\usepackage{titlesec}
\usepackage{layout}
\usepackage{fontawesome}
\usepackage[breaklinks]{hyperref}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{graphicx}

\geometry{
    left=20pt,
    right=20pt,
    top=20pt,
    bottom=20pt,
}

%-------------------------------------------------------------------------------
%                Global Fonts
%-------------------------------------------------------------------------------
\newcommand{\fontExtraLargeBold}[1]{{\fontsize{30}{36}\selectfont\bfseries #1}}
\newcommand{\fontExtraLargeRegular}[1]{{\fontsize{30}{36}\selectfont #1}}
\newcommand{\fontExtraLargeItalics}[1]{{\fontsize{30}{36}\selectfont\itshape #1}}

\newcommand{\fontLargeBold}[1]{{\fontsize{20}{24}\selectfont\bfseries #1}}
\newcommand{\fontLargeRegular}[1]{{\fontsize{20}{24}\selectfont #1}}
\newcommand{\fontLargeItalics}[1]{{\fontsize{20}{24}\selectfont\itshape #1}}

\newcommand{\fontMediumBold}[1]{{\fontsize{15}{18}\selectfont\bfseries #1}}
\newcommand{\fontMediumRegular}[1]{{\fontsize{15}{18}\selectfont #1}}
\newcommand{\fontMediumItalics}[1]{{\fontsize{15}{18}\selectfont\itshape #1}}

\newcommand{\fontSmallBold}[1]{{\fontsize{10}{12}\selectfont\bfseries #1}}
\newcommand{\fontSmallRegular}[1]{{\fontsize{10}{0pt}\selectfont #1}}
\newcommand{\fontSmallItalics}[1]{{\fontsize{10}{12}\selectfont\itshape #1}}

\newcommand{\fontExtraSmallBold}[1]{{\fontsize{8}{10}\selectfont\bfseries #1}}
\newcommand{\fontExtraSmallRegular}[1]{{\fontsize{8}{10}\selectfont #1}}
\newcommand{\fontExtraSmallItalics}[1]{{\fontsize{8}{10}\selectfont\itshape #1}}


\definecolor{sectionheadercolor}{RGB}{30, 144, 255}



% Gray-scale colors
\definecolor{white}{HTML}{FFFFFF}
\definecolor{black}{HTML}{000000}
\definecolor{darkgray}{HTML}{333333}
\definecolor{gray}{HTML}{414141} %414141
\definecolor{lightgray}{HTML}{999999}
% Basic colors
\definecolor{green}{HTML}{C2E15F}
\definecolor{orange}{HTML}{FDA333}
\definecolor{purple}{HTML}{D3A4F9}
\definecolor{red}{HTML}{FB4485}
\definecolor{blue}{HTML}{4472c4}
% Text colors
\definecolor{darktext}{HTML}{414141} % Highlighted grey headings
\colorlet{text}{black}
\colorlet{graytext}{gray}
\colorlet{lighttext}{black}
\colorlet{sectiondivider}{gray}
% russell colors
\definecolor{russell-emerald}{HTML}{00A388}
\definecolor{russell-skyblue}{HTML}{0395DE}
\definecolor{russell-red}{HTML}{DC3522}
\definecolor{russell-purple}{HTML}{A32CC4}
\definecolor{russell-pink}{HTML}{EF4089}
\definecolor{russell-orange}{HTML}{FF6138}
\definecolor{russell-nephritis}{HTML}{27AE60}
\definecolor{russell-concrete}{HTML}{95A5A6}
\definecolor{russell-darknight}{HTML}{131A28}
\definecolor{russell-black}{HTML}{000000}
\colorlet{russell}{russell-red}

% Boolean value to switch section color highlighting
\newbool{acvSectionColorHighlight}
\setbool{acvSectionColorHighlight}{true}

% russell section color
\def\@sectioncolor#1#2#3{%
  \ifbool{acvSectionColorHighlight}{{\color{russell}#1#2#3}}{#1#2#3}%
}

\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

%-------------------------------------------------------------------------------
%                Configuration for colors
%-------------------------------------------------------------------------------




\begin{document}
%-------------------------------------------------------------------------------
% HEADER
%-------------------------------------------------------------------------------
\begin{center}
  \fontLargeBold{NISHANT KANT OJHA} \\
  \fontExtraSmallRegular{\faEnvelope\hspace{2pt} nishantkantojha@outlook.com $|$ 	\hspace{2pt}\faGithub\hspace{2pt} \href{https://github.com/thevedicdeveloper}{@vedicdeveloper} $|$ \hspace{2pt}\faMapMarker\hspace{2pt} \href{https://maps.app.goo.gl/3KBkGrLHVfiQRCgh7}{Toronto, Ontario}}
\end{center}  


%-------------------------------------------------------------------------------
% PROFESSIONAL SUMMARY
%-------------------------------------------------------------------------------
\vspace{10pt}\fontMediumBold{\texorpdfstring{\textcolor{blue}{PROFESSIONAL SUMMARY {\color{black}\hrulefill}}}{PROFESSIONAL SUMMARY}}\vspace{5pt}\\
\fontSmallRegular{With over 5 years of experience as a Frontend Developer specializing in Angular, I bring a mix of tech know-how and problem-solving skills to projects. From making user interfaces easy to use to boosting performance, I love tackling challenges and finding smart solutions. I keep up with the latest in Angular to deliver top-notch work. With a track record of success and a drive to keep improving, I'm ready to make a big difference on any frontend team.}


%-------------------------------------------------------------------------------
% CERTIFICATIONS
%-------------------------------------------------------------------------------
\vspace{10pt}\fontMediumBold{\texorpdfstring{\textcolor{blue}{CERTIFICATIONS {\color{black}\hrulefill}}}{CERTIFICATIONS}}\vspace{5pt}\\
\fontSmallRegular{\textbf{AZ-104} : Microsoft Azure Administration Associate}  \hfill{Jul, 2022} \\
\fontSmallRegular{\textbf{AZ-204} : Microsoft Azure Developer Associate} \hfill{Jun, 2022} \\
\fontSmallRegular{\textbf{AZ-900} : Microsoft Azure Fundamentals}  \hfill{Mar, 2022} \\
\fontSmallRegular{\textbf{DP-900} : Microsoft Azure Data Fundamentals}  \hfill{Mar, 2022}


%-------------------------------------------------------------------------------
% SKILLS
%-------------------------------------------------------------------------------
\vspace{10pt}\fontMediumBold{\texorpdfstring{\textcolor{blue}{SKILLS \textcolor{black}{\hrulefill}}}{SKILLS}}\vspace{5pt}
\setlength{\tabcolsep}{0pt}
\begin{tabular}{@{}p{0.23\linewidth}@{\hspace{5pt}}p{0.75\linewidth}@{}}
\textbf{Languages} & {C\#, TypeScript, JavaScript, Python, GraphQL, Bash, C, C++, Java, Groovy, LaTeX, Yaml} \\
\textbf{Frameworks \& Runtime Envs} & {\href{https://angular.io/}{Angular}, \href{https://dotnet.microsoft.com/apps/aspnet}{ASP.NET Core}, \href{https://reactjs.org/}{React}, Node.js, CLR, Containerd, JRE} \\
\textbf{Angular Libraries} & {Microsoft Authentication Library (MSAL), Angular Fire, Angular Google Maps, Angular Google Pay, Angular CDK, Angular Material, Angular YouTube, i18n, NgRx, AG Grid, ngx-translate, ngx-mask, \href{https://swimlane.github.io/ngx-charts/}{ngx-charts}} \\
\textbf{UI Libraries} & {\href{https://getbootstrap.com/}{Bootstrap}, \href{https://material.angular.io/}{Angular Material}, \href{https://tailwindcss.com/}{Tailwind CSS}}\\
\textbf{PDF's \& Charting Libraries} & {\href{https://www.chartjs.org/}{chart.js}, \href{https://d3js.org/}{D3.js}, \href{https://mozilla.github.io/pdf.js/}{pdf.js},  \href{https://github.com/parallax/jsPDF}{jsPDF}}\\
\textbf{Testing Libraries} & {Karma, Protractor, Jest, Cypress, Mocha, Jasmine} \\
\textbf{Other Libraries} & {\href{https://rxjs.dev/}{RxJs}. Storybook, Three.js, leaflet.js, SendGrid, \href{https://lodash.com/}{Lodash},  \href{https://momentjs.com/}{Moment}, webpack, eslint, underscore.js}\\
\textbf{Database} & {MSSQL, MySQL, PostgreSQL, SQLite, MongoDB, Redis, Firebase, Supabase, Appwrite, Local \& Session Storage, IndexedDB} \\
\textbf{Azure Services} & {App Service, Static Web Apps, Functions, Blob Storage, Azure CDN, Azure API Management, Key Vault, Application Insights, Active Directory, Docker, Kubernetes, Ansible, GitHub Actions, Azure DevOps, JFrog, Splunk} \\
\textbf{Development Tools} & {Figma, Postman, Visual Paradigm, Matrix, Putty, WinScp, Powershell, Git, GitHub, Jira Work Management, Confluence, Vim, Neo Vim} \\
\end{tabular}\\


%-------------------------------------------------------------------------------
% PROFESSIONAL EXPERIENCE
%-------------------------------------------------------------------------------
\vspace{10pt}\fontMediumBold{\texorpdfstring{\textcolor{blue}{PROFESSIONAL EXPERIENCE \textcolor{black}{\hrulefill}}}{PROFESSIONAL EXPERIENCE}}\vspace{5pt}\\
\textbf{Full Stack Developer} $|$ Securian Canada \hfill {Jan, 2022 - Present}\\
\textbf{Ori} - A single-page web app used by banks like BMO to streamline operations.
\vspace{-5pt}\begin{itemize}[leftmargin=15pt, itemsep=-5pt]
    \item Effectively collaborated with Business Analysts, Product Owners, and Product Managers to create comprehensive Business Requirement Documents (BRDs).
    \item Organized the web application project structure by dividing it into API, Application, Domain, and Infrastructure layers.
    \item Integrated the application with major third-party providers like Canada Post, SharePoint, Equifax, and TransUnion, enhancing data integration capabilities, and partnered with Cumis Credit Insurance for quoting, streamlining the insurance quoting process.
    \item Configured dozens of APIs using GraphQL, optimizing data handling and communication across the platform.
    \item Developed over 50 RESTful APIs, interfacing with MSSQL databases using Microsoft EF Core and LINQ for CRUD operations, and wrote complex SQL queries for SQL Server databases.
    \item Designed and implemented five scalable microservices using ASP.NET Core Web API and GraphQL, and deployed them to Azure Web App Services via Azure DevOps.
    \item Utilized advanced C\# features to build high-performance applications, including multi-threading, exception handling, logging, and asynchronous function handling.
    \item Configured global logging mechanisms in ASP.NET web applications using ILogger, and integrated logging with Azure Application Insights for troubleshooting and performance analysis.
    \item Implemented API validation using the Fluent Validation library, enhancing API security.
    \item Integrated Azure Application Insights into the frontend Angular application for enhanced monitoring and performance tracking.
    \item Developed and tested UI components with Storybook, reducing UI bugs by 30\%, and improved reliability and stability through comprehensive Angular testing using Karma.
    \item Integrated RESTful APIs with frontend applications for efficient data retrieval and synchronization.
    \item Implemented ASP.NET Core Identity features for authentication, authorization, and access control, integrating OAuth2 and JWT token-based authorization.
    \item Conducted comprehensive unit testing and integration testing for web applications using xUnit and NLog, ensuring high-quality code and robust software solutions. Created detailed test cases to validate functionalities and maintain a high level of application stability throughout the development process.
    \item Developed insightful dashboards with Chart.js and D3.js, enhancing user experience.
    \item Configured more than a dozen CI/CD pipelines in Azure DevOps for building, testing, scanning, releasing, and deploying applications/microservices to Azure Web Apps and Blob Storage.
    \item Deployed .NET applications to production in Azure cloud environments, supporting production activities and collaborating with DevOps teams to improve deployment speed.
    \item Implemented advanced source control branching strategies to deploy different application versions to production, optimizing cost management and infrastructure utilization.
    \item Adhered to Agile methodology by participating in daily scrum meetings and utilizing JIRA for managing user stories and bug tracking, enabling effective collaboration with cross-functional teams and ensuring a smooth and transparent development workflow.
\end{itemize}

% NOVA
\textbf{Nova} - Securian Canada insurance distribution platform used by major credit unions.
\vspace{-5pt}\begin{itemize}[leftmargin=15pt, itemsep=-5pt]
    \item Integrated Microsoft Authentication Library (MSAL) for secure authentication and authorization, achieving a 99.9\% authentication success rate.
    \item Created an Azure function in C\# for document uploads to Azure Blob Storage using Azure SDK, improving handling efficiency by 50\%.
    \item Established Angular state management using NgRx from scratch, reducing data retrieval times by 40\% and creating a more scalable architecture.
    \item Implemented Angular UI components with Storybook, for isolated UI Component development and testing, which resulted in reducing UI bugs by 30\%.
    \item Enhanced code quality and reduced review times by 30\% by writing out ESLint ruels for the Angular project.
    \item Collaborated with Canada Life Credit Union for insurance quoting, extending the platform's functionality and reach.
\end{itemize}

% CREDITOR INSURANCE 
\textbf{Creditor Insurance Discovery Tool} - A single-page web app used by banks like BMO to streamline operations.
\vspace{-5pt}\begin{itemize}[leftmargin=15pt, itemsep=-5pt]
      \item Designed dynamic Angular forms based on user interaction.
      \item Implemented Adobe PDF SDK, Azure Blob Storage, and Functions for efficient PDF generation and data storage.
      \item Expanded language support from 2 to 5 using Angular i18n, enhancing accessibility.
      \item Developed a responsive and user-friendly interface using Angular Material and dynamic tooltips.
      \item Improved code quality and reduced review times by 30\% through ESLint integration.
\end{itemize}


%-------------------------------------------------------------------------------
% FREELANCE EXPERIENCE
%-------------------------------------------------------------------------------
\vspace{10pt}\fontMediumBold{\texorpdfstring{\textcolor{blue}{FREELANCE EXPERIENCE \textcolor{black}{\hrulefill}}}{FREELANCE EXPERIENCE}}\vspace{5pt}\\
\textbf{PixleForge Solutions} | Upwork Inc. \hfill {Marc, 2020 - Feb, 2022}
\vspace{-5pt}\begin{itemize}[ leftmargin=15pt, itemsep=-5pt]
      \item Collaborated closely with design and product teams, leveraging Angular's reactive forms and observables to enhance UX, resulting in a 25\% increase in user engagement.
      \item Integrated RESTful interfaces with ASP.NET Web API endpoints, reducing API response time by 40\% and ensuring seamless frontend-backend communication.
      \item Decomposed projects using Angular's modular architecture, improving project delivery timelines by 30\%.
      \item Implemented features with Angular's dependency injection, reducing post-launch defects by 50\%.
      \item Documented technical details using Angular's documentation generation tools and ASP.NET Core's logging capabilities, increasing development efficiency by 20\%.
      \item Employed Angular's routing and state management features to improve system stability by 30\%.
      \item Stayed updated with latest technologies, driving a 15\% increase in team productivity by exploring Angular and ASP.NET Core advancements.
  \end{itemize}


%-------------------------------------------------------------------------------
% PERSONAL PROJECTS
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
% ACADEMIC PROJECTS
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
% EDUCATION
%-------------------------------------------------------------------------------
\vspace{10pt}\fontMediumBold{\texorpdfstring{\textcolor{blue}{EDUCATION {\color{black}\hrulefill}}}{EDUCATION}}\vspace{5pt}\\
\textbf{Diploma in Computer Programming} $|$ Seneca College $|$ GPA - 3.8 \hfill Jan, 2021 - Aug, 2022 \\
\textbf{Course Highlights:}
\vspace{-5pt}\begin{itemize}[leftmargin=15pt, itemsep=-5pt]
  \item Developed object-oriented programming skills using C/C++
  \item Manipulated data using SQL for efficient database management
  \item Modeled, designed, and developed databases for business purposes
  \item Engineered software and hardware systems for creating data communication networks
  \item Applied principles of the Software Development Life Cycle (SDLC), Computer Networking, System Design, and UML
  \item Authored shell scripts, utilized pipes and redirection for data manipulation, and defined patterns using regex
  \item Practiced DevOps principles, including Source Control Management, Integration, Testing, Configuration Management, and Monitoring
\end{itemize}

%-------------------------------------------------------------------------------
% INTERESTS
%-------------------------------------------------------------------------------
\vspace{10pt}\fontMediumBold{\texorpdfstring{\textcolor{blue}{INTERESTES \textcolor{black}{\hrulefill}}}{INTERESTES}}\vspace{5pt}
\vspace{-5pt}\begin{itemize}[leftmargin=15pt, itemsep=-5pt]
  \item Experimenting with \textbf{cooking} techniques and creating new recipes.
  \item Cultivating a variety of plants and maintaining a \textbf{garden}, currently growing Aloe Vera and Basil.
  \item Solving complex problems in \textbf{mathematics}.
  \item Exploring the principles and theories of \textbf{physics}.
  \item Improving \textbf{typing} speed and accuracy.
  \item Competing in multiplayer battleground games like \textbf{COD} and \textbf{PUBG}.
  \item Learning and playing \textbf{musical instruments}, currently mastering the \textbf{kartal}.
\end{itemize}
\end{document}
